---
title: "Popular Music Analysis"
subtitle: 'Kay Royo, Ibrahim Rizk, Aurian Saidi'
output: rmdformats::robobook
---

```{css, echo=FALSE}
h1, h2, h3 {
  text-align: center;
}
```

# Introduction 

The role of music in our lives is significant, as it impacts our emotions, physical health, and social connections. It has the ability to elicit various emotions and moods, which can create a sense of connection within ourselves and with others. Depending on the type of music and our individual experiences, music can provide comfort, joy, or even sadness. Music also offers physical and psychological benefits, such as stress and anxiety reduction, blood pressure regulation, and cognitive function improvement. Whether we are passive listeners or actively involved in creating or performing music, it can enhance our lives in numerous ways.

The purpose of this study is to analyze popular music to investigate the songs that are widely consumed and appreciated across the globe. This study encompasses various methods that aim to comprehend the different components of present-day popular music. As the role of popular music in our society continues to evolve, popular music analysis has emerged as a crucial field of study over the past few decades. Through examining popular music, scholars and researchers can gain valuable insights into the cultural, social, and political factors that shape the music we listen to. Furthermore, by examining the musical styles, themes, and lyrics of popular music in different countries, we can acquire a better understanding of the values and beliefs of those cultures. The study seeks to address the following questions of interest.

- Which attributes of a song have a relationship with a song’s popularity? 

-	What is the prevailing sentiment or emotional tone of popular songs in various countries?

- To what extent do music preferences align across different countries based on current trends? 



# Background 

In recent years, the analysis of popular music in various countries has gained significance due to the ease of accessing and sharing music across borders facilitated by global communication and technology. This growing interest among scholars and researchers aims to explore the diverse musical traditions and practices of different countries while understanding the cultural, social, and political contexts in which popular music is created and consumed.

Research on popular music in different countries typically concentrates on the distinct musical styles, themes, and lyrics that reflect the cultural traditions and values of those societies. It may also investigate how music expresses social and political messages and promotes cultural and national identities. Additionally, analyses of popular music in different countries may examine how global musical trends and influences are adapted and transformed within local contexts, as well as how music is utilized to resist dominant cultural or political forces. In general, the study of popular music in different countries is a vibrant and diverse field that provides insights into the unique musical cultures and practices of different regions, and how music is utilized to express and shape social, cultural, and political identities.

# I. Data Collection 

```{r, echo=FALSE}
htmltools::includeHTML("../Data/Data_Collection.html")
```

# II. Data Preprocessing

```{r, echo=FALSE}
htmltools::includeHTML("../Data/Data_Processing.html")
```

# III. Exploratory Analysis 

# IV. Classification  

# V. Clustering 

```{r, echo=FALSE}
htmltools::includeHTML("../Clustering/Clustering.html")
```

# VI. Sentiment Analysis 


```{r, echo=FALSE}
htmltools::includeHTML("../Sentiment_Analysis/Sentiment_Analysis.html")
```

# Conclusion

(Insert conclusion regarding EDA and Classification)

After performing an agglomerative clustering of the data, we can conclude that there are several reasons that contribute to similarity in trending music taste. First, the geographic proximity of countries can result in shared cultural influences that manifest within popular music. Second, culture can also play a significant role in music preferences, as countries with similar cultural backgrounds might have a stronger affinity towards specific genres or artists. Finally, language has a powerful affect on music similarity that is supplemented by the previous geographical and cultural factors.

Based on the results obtained using different methods to analyze the most common sentiment or emotions, it can be concluded that the lyrics of popular songs generally convey a positive sentiment. There are several reasons why people tend to enjoy listening to songs with positive sentiment. Firstly, such songs can create a sense of happiness, joy, and optimism, which can be uplifting and improve one's mood. This is particularly true when an individual is experiencing challenging situations or negative emotions. Secondly, positive songs often have catchy melodies and upbeat rhythms that can make them more enjoyable to listen to, and people may find themselves singing or humming along with them. Thirdly, songs with positive sentiments can provide a sense of hope and inspiration, motivating people to pursue their goals and dreams. Finally, positive songs may serve as a reminder of happy memories or experiences, allowing people to relive those moments through the music. Overall, listening to songs with positive sentiments can have a significant impact on an individual's mood, outlook on life, and overall well-being. Therefore, it is logical to conclude that individuals across the globe would have a preference for songs that convey positive sentiments.

# References 

Spotify. (n.d.). Spotify Charts. Retrieved March 14, 2023, from https://charts.spotify.com/home

Spotify. (n.d.). Web API Reference. Spotify Developer. Retrieved March 14, 2023, from https://developer.spotify.com/documentation/web-api/reference/#/

Genius. (n.d.). Genius API Documentation. Genius. Retrieved March 14, 2023, from https://docs.genius.com/

Millr, J. (n.d.). LyricsGenius: a Python client for the Genius.com API. GitHub. Retrieved March 14, 2023, from https://github.com/johnwmillr/LyricsGenius

Mohammad, S. (n.d.). NRC Emotion Lexicon. Retrieved March 14, 2023, from http://saifmohammad.com/WebPages/NRC-Emotion-Lexicon.htm

Hutto, C.J. (2014). vaderSentiment. [Computer software]. Retrieved from https://github.com/cjhutto/vaderSentiment

TextBlob. (n.d.). TextBlob documentation. TextBlob. https://textblob.readthedocs.io/en/dev/

# Appendix 

## [Github Repository](https://github.com/kayannr/STA141B) 

## Team Members and Responsibilities 

Tasks Completed     Kay Royo                  Ibrahim Rizk               Aurian Saidi
------------------  ------------------------- -------------------------- ---------------------------------- 
Code                  Data Collection          Clustering                EDA
                      Data Preprocessing                                 Classification
                      Sentiment Analysis 
Presentation          Data Collection          Clustering                Intro 
                      Data Preprocessing       Conclusion                EDA
                      Sentiment Analysis                                 Classification
Report                Introduction             Clustering
                      Background               Conclusion
                      Data Collection
                      Data Preprocessing
                      Sentiment Analysis
                      Conclusion 
                      References 
                      Report Style
          