---
title: "Popular Music Analysis"
subtitle: 'Kay Royo, Ibrahim Rizk, Aurian Saidi'
output: rmdformats::robobook
---

```{css, echo=FALSE}
h1, h2, h3 {
  text-align: center;
}
```

# Introduction 

# I. Data Collection 

```{r, echo=FALSE}
htmltools::includeHTML("../Data/Data_Collection.html")
```

# II. Data Preprocessing

```{r, echo=FALSE}
htmltools::includeHTML("../Data/Data_Processing.html")
```

# III. Exploratory Analysis 

# 1V. Clustering 

# V. Sentiment Analysis 


```{r, echo=FALSE}
htmltools::includeHTML("../Sentiment_Analysis/Sentiment_Analysis.html")
```

# Conclusion


# References 

# Appendix 

## Team Members and Responsibilities 

Team member         Tasks Completed 
------------------  ------------------------------------------------------------------------------------- 
Kay Royo            Data Collection, Data Preprocessing, Sentiment Analysis, Presentation Slides, Report  
Aurian Saidi        Presentation Slides, Report  
Ibrahim Rizk        Clustering, Presentation Slides, Report  

